### 2013-11-12 notes/notes.tex
changes

>>>>

\section{To add on proposal}

\subsection{a good intro}
Coalition-game thoery provides suitable analytical tools that have been widely explored in different diciplines such as economics and political sceince. With the recent emergence of cooperation as a new networking paradigm, coalition-game  theory started to become a central framework for modeling cooperation in wireless and communication networks. For instance, coalition games prove to be a very powerful tool for designing fair, robust, practical and efficient cooperation strategies in communication networks.

\subsection{contractnet}

Using round robin instead of contractnet, to reduce the simulation complexity. Both have identical behavoiurs.
we dont want WS not bid if they are not working at that moment.

\subsection{other}

adding "`towards defingin and assessing the non-functional properties of communities of web services"' as good refrence for QoS metrics.

adding a tree chart of what we cover in proposed method section.

adding shapely value properties.
